---
title: "Problems and Solutions to Compile a PDF Version of Advanced R"
author: "Liu Lijiao"
date: "2020/3/20"
output: pdf_document
---


During the building process,I have met many problems,the followings are the errors I've met and how I solved them.

# Quitting from lines 223-235 (Introduction.Rmd)

```{r eval=FALSE}
Adding'encoding = "UTF-8"' in line 224
```

# Quitting from lines 80-81 (Names-values.Rmd) 

```{r eval=FALSE}
install.packages("lobstr")
```

# Quitting from lines 233-234 (Perf-measure.Rmd) 

```{r eval=FALSE}
install.packages("ggfortify")
```

# Missing Packages

```{r eval=FALSE}
Most of the errors are packages missing.
```

I had been installing the required packages until I met these issues:

#Quitting from lines 77-84(Rcpp.Rmd)

```{r eval=FALSE}
I install Rtools to my computer.
```

# '"xelatex"' not found

```{r eval=FALSE}
I install MiKTeX and choose "Always install missing packages on-the-fly" in the process.
```

# About Font

```{r eval=FALSE}
I download the font 'inconsolata'and'andalemono'from the internet.
```

Finally,this book was successfully built by installing the required packages and searching online.
